Total Platform Cyber Protection

### 2016-08-21 paper.tex
definitely solved the biblio prob

Most research into hardware Trojans deal with using side-channel
analysis to identify the malicious Trojan behavior~\cite{lee2005,
agrawal2007,banga2008,banga2008a,jin2008,du2010,narasimhan2011,
narasimhan2012,cao2013,davoodi2013,dworak2013,forte2013,
liu2013,liu2014,bao2015}. This research uses power analysis, heat
analysis, or other side-effects to determine that the hardware is
executing abnormal logic. Unfortunately, this typically requires
building a model based on a ``golden'' or known-good hardware, which
is often not accessible. Furthermore, as chips become more complex,
the Trojan logic become an increasingly smaller portion of the chip,
which in turn reduces the side-channel behavior of the chip
significantly.

Other research has demonstrated the attacks that are possible by
actually implementing Trojan behavior~\cite{king2008,jin2010,
sturton2011,liu2013,jin2014,zhang2014}. This line of research
shows that Trojan logic is feasible for an attack.

@@

Another avenue of research is to change the design of the chip itself,
in order to improve the testability of the chip or to increase the
effectiveness of the side-channel analysis~\cite{chakraborty2008,
li2008,salmani2009,hicks2010,rosenfeld2011,waksman2011,
bhunia2013,davoodi2013,rajendran2013,rolt2014}. This line of
research attempts to rethink designing the hardware itself. However, a
major drawback is that this can increase the cost of the hardware and
it must be somehow mandated to be used in COTS components.

@@

Finally, there are several surveys conducted on hardware security,
which provide a good overview of the field~\cite{wang2008,
tehranipoor2010,guin2014,guin2014a,guin2014b}.

@@

\subsection{Research}
%Faris: Some fixes below. 
Researchers have attempted to identify real-world attacks on firmware
code~\cite{tsow2006,cui2010,duflot2011,basnight2013,cui2013,
zaddach2013,zaddach2013a,maskiewicz2014,stuttgen2015}. These
attacks are particularly effective, and researchers have shown that
these are able to persist through a reboot and cannot be detected by
the upper layers.

@@

Another approach includes runtime monitoring into the
firmware, so that compromises can be detected~\cite{cui2010a,
cui2011}. This approach is further complicated by the lack of
abstractions in the firmware environment.

>>>>

Most research into hardware Trojans deal with using side-channel
analysis to identify the malicious Trojan behavior~\cite{lee2005,agrawal2007,banga2008,banga2008a,jin2008,du2010,narasimhan2011,narasimhan2012,cao2013,davoodi2013,dworak2013,forte2013,liu2013,liu2014,bao2015}. This research uses power analysis, heat
analysis, or other side-effects to determine that the hardware is
executing abnormal logic. Unfortunately, this typically requires
building a model based on a ``golden'' or known-good hardware, which
is often not accessible. Furthermore, as chips become more complex,
the Trojan logic become an increasingly smaller portion of the chip,
which in turn reduces the side-channel behavior of the chip
significantly.

Other research has demonstrated the attacks that are possible by
actually implementing Trojan behavior~\cite{king2008,jin2010,sturton2011,liu2013,jin2014,zhang2014}. This line of research
shows that Trojan logic is feasible for an attack.

@@

Another avenue of research is to change the design of the chip itself,
in order to improve the testability of the chip or to increase the
effectiveness of the side-channel analysis~\cite{chakraborty2008,li2008,salmani2009,hicks2010,rosenfeld2011,waksman2011,bhunia2013,davoodi2013,rajendran2013,rolt2014}. This line of
research attempts to rethink designing the hardware itself. However, a
major drawback is that this can increase the cost of the hardware and
it must be somehow mandated to be used in COTS components.

@@

Finally, there are several surveys conducted on hardware security,
which provide a good overview of the field~\cite{wang2008,tehranipoor2010,guin2014,guin2014a,guin2014b}.

@@

\subsection{Research}
%Faris: Some fixes below. 
Researchers have attempted to identify real-world attacks on firmware
code~\cite{tsow2006,cui2010,duflot2011,basnight2013,cui2013,zaddach2013,zaddach2013a,maskiewicz2014,stuttgen2015}. These
attacks are particularly effective, and researchers have shown that
these are able to persist through a reboot and cannot be detected by
the upper layers.

@@

Another approach includes runtime monitoring into the
firmware, so that compromises can be detected~\cite{cui2010a,cui2011}.
This approach is further complicated by the lack of
abstractions in the firmware environment.
